Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-20 doc/PRF2022/PRF_main.tex
reordered figures, added insets

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 198 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}\\
  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

@@

\section{Results}
\label{sec:results}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in shear flow}
\end{figure}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
\end{figure}
\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

@@

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

>>>>

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.49\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.49\textwidth]{Nb198b_eta.pdf}\\
  \includegraphics[width=0.49\textwidth]{Nb198c_eta.pdf}
  \includegraphics[width=0.49\textwidth]{Nb198d_eta.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles selc-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
%  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
  %  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
  Panel (b): same but for order parameters 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

@@

\section{Results}
\label{sec:results}

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    The figure shows a vesicle in shear flow (panels (a)-(d), $\dot \gamma = ...$) 
    and the multiple component bilayers in shear (panels (e)-(f), $\dot \gamma = ...$).}
\end{figure}

\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

@@

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    The quantities $E(t)$, $\tilde S_2(t)$, and $d(t)$
    are indicators of bilayer (case (i)) deformation at various shear rates. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{vesTG_0.png}
  \includegraphics[width=0.32\textwidth]{vesTG_2500.png}
  \includegraphics[width=0.32\textwidth]{vesTG_5000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

%

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%

@@

%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}
